Mitigating (D)DoS in Named-Data Networking

### 2012-11-27 paper.tex
Add stats algorithm's pseudocode. "A little bit" overcomplicated right now
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@813 df1a90cd-247b-4364-bdaf-287a704eb499
Small update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@814 df1a90cd-247b-4364-bdaf-287a704eb499
Adding fair-queueing algorithm description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@815 df1a90cd-247b-4364-bdaf-287a704eb499
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-b

\documentclass[conference]{IEEEtran}
\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}
\date{}
\begin{document}
\maketitle

@@

\section {Evaluation}
 Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).

\subsection{Simulation versus Emulation}
Results establishing validity of  simulator.

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
\framebox{\begin{minipage}[c]{0.40 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
\framebox{\begin{minipage}[c]{0.42 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\begin{document}
\maketitle

@@

\section {Evaluation}
\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}

We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways. First, we need to understand how each method works on a very ground level of a just few nodes and links. Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes. To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy. As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.

\input{simulation-emulation.tex}

@@

\input{large-scale.tex}

@@

\appendix

\input{algos/physical-limits.tex}

\input{algos/fair-queueing.tex}

\input{algos/dynamic-limits.tex}

\input{algos/probabilistic.tex}

\input{algos/stats.tex}
